\documentclass[12pt]{letter}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage{setspace}
\usepackage{parskip}

\begin{document}

\begin{letter}{
The Class Teacher,\\
MIT World Peace University,\\
Fourth Year B.Tech \\ Computer Science Engineering - Cybersecurity and Forensics,\\
Panel A.}

\opening{Respected Sir}

I hope this letter finds you well. I am writing to humbly request your kind consideration regarding the attendance shortfall I am currently facing. I am a student of Fourth Year B.Tech in Computer Science Engineering, Panel A, and I would like to bring to your attention the reasons behind my inability to meet the \textbf{75\% attendance criteria.}

From \textbf{January 1\textsuperscript{st} to February 1\textsuperscript{st}}, I was deeply engaged in preparing for the \textbf{GATE 2025} examination, which is a crucial step towards my aspiration of pursuing higher studies. The preparation required focused and uninterrupted effort, leading me to prioritize self-study during this period.

Subsequently, during the \textbf{end of February and the first week of March}, I had two off-campus interview processes for which I had to prepare rigorously and attend selection rounds. This additional commitment further extended my absence from regular classes.

Due to these academic and professional obligations, I was unable to attend classes consistently over a span of approximately \textbf{1.5 months}. I have attached all relevant documents including GATE admit card and interview call E-mails for your reference.

I sincerely assure you that I remain committed to my academic responsibilities and have been keeping up with the coursework through self-study and peer discussions. I respectfully request you to kindly grant me relief in the attendance requirement and allow me to continue with the semester and maintain my scholarship without any hindrance.

I shall remain grateful for your understanding and support.

\closing{Thanking you,\\
Yours sincerely,\\[1em]
\textbf{Krishnaraj Thadesar}\\
1032210888, \\
PA15 \\
Fourth Year B.Tech (CSF), Panel A, \\
MIT World Peace University}

\end{letter}

\end{document}
